```{r, include = FALSE}
if (!exists("AnVIL_module_settings")) {
  AnVIL_module_settings <- list(
    cloud_environment = "your cloud environment"
    )
} else if (is.null(AnVIL_module_settings$cloud_environment)) {
  AnVIL_module_settings$cloud_environment = "your cloud environment"
}
```

Cloud computing costs are based on the amount of time you use the computing resources, so it's important to clean up after yourself when you're done, and not just leave the computers running.

There are two ways to "shut down" `r AnVIL_module_settings$cloud_environment` on AnVIL:

- **Pause** the environment: This will save a copy of your work, and then release the computers for other people to use them.  **Do this if you plan to continue working in `r AnVIL_module_settings$cloud_environment`**.
    - It's similar to turning off your computer or phone - when you start it back up, everything will be where you left it.
    - This still costs a small amount of money, but much less than leaving the computer running.  
- **Delete** the environment: This will delete everything and then release the computers for other people to use them.  **Do this if you are completely finished working**, or if your future work will be in a new environment.
    - It's similar to throwing your computer or phone in the trash!
    - **You will not be able to recover your work.**
    - Make sure you have saved anything you need to another location (such as the Workspace bucket, GitHub, or your local machine) before you delete your environment.

```{r, include = FALSE}
AnVIL_module_settings <<- NULL
```
