```{r echo = FALSE}
knitr::opts_chunk$set(out.width = "100%")
```

# Billing

Modules about billing and Billing Projects on Google Cloud Platform and Terra.

<br>

## Create Google Billing Account

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_google_billing_create_account.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Add Terra to Google Billing Account

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_google_billing_add_terra.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Add Members to Google Billing Account

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_google_billing_add_member.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Set Alerts for Google Billing

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_google_billing_set_alerts.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## View Spend for Google Billing

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_google_billing_view_spend.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Create Terra Billing Project

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_terra_billing_project_create.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Add Member to Terra Billing Project

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_terra_billing_project_add_member.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Disable Terra Billing Project

By default this module includes a warning to make sure people understand they will lose access to their Workspace buckets. You can remove the warning from this module by setting `AnVIL_module_settings$warning` to `FALSE` before running `cow::borrow_chapter`:

```
AnVIL_module_settings <- list(
  warning = FALSE
)
cow::borrow_chapter(
  doc_path = "child/_child_terra_billing_project_disable.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_terra_billing_project_disable.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::
