# Billing

Modules about billing and Billing Projects on Google Cloud Platform and Terra.

<br>

## Create Google Billing Account

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_google_billing_create_account.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Add Terra to Google Billing Account

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_google_billing_add_terra.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Create Terra Billing Project

This module can be modified depending on the audience:

- If `AnVIL_module_settings$google_billing` is set to `TRUE`, it assumes the audience is also involved in Google Billing and reminds them to use the same Google Account to access Terra
- If `AnVIL_module_settings$google_billing` is `FALSE` or absent, the reminders are not included

The demo below has the reminders included

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
# Specify settings
AnVIL_module_settings <- list(
  google_billing = TRUE
)
cow::borrow_chapter(
  doc_path = "child/_child_terra_create_billing_project.Rmd",
  branch = "update-child-create-billing-project",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Add Members to Google Billing Account

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_google_billing_add_member.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Set Alerts for Google Billing

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_google_billing_set_alerts.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## View Spend for Google Billing

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_google_billing_view_spend.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

