# Student instructions

Modules aimed at students in a course or workshop.
 
<br>
 
## Student Account Setup
 
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_student_create_account.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

## Student instructions for cloning a Workspace

These instructions can be customized to a specific workspace by setting certain variables before running `cow::borrow_chapter()`.  If these variables have not been set, reasonable defaults are provided (e.g. "ask your instructor").

### With no variables set:

```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_student_workspace_clone.Rmd",
  branch = "student-clone",
  repo_name = "jhudsl/AnVIL_Template"
)
```

### With variables set:

```{r, echo = FALSE, results='asis'}
workspace_name <- "Example_Workspace"
workspace_link <- "http://example.com/"
billing_project <- "Example Billing Project"

cow::borrow_chapter(
  doc_path = "child/_child_student_workspace_clone.Rmd",
  branch = "student-clone",
  repo_name = "jhudsl/AnVIL_Template"
)
```
