# Student instructions

Modules aimed at students in a course or workshop.
 
<br>
 
## Student Account Setup
 
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_student_create_account.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

## Student instructions for launching RStudio

These instructions can be customized by setting certain variables before running `cow::borrow_chapter()`.

- If no variables are set, general purpose instructions with advice about choosing an environment will be used
- If `audience` is set to "student", it gives more specific instructions.
  - With no further informationc, it will tell them to use the default RStudio settings
  - If `docker_image` or `startup_script` are set, it will tell them to open the customization dialogue and direct them on how to set the image and/or script.

### Using default environment:

```{r, echo = FALSE, results='asis'}
AnVIL_module_settings <- list(
  audience = "student",
)

cow::borrow_chapter(
  doc_path = "child/_child_rstudio_launch.Rmd",
  branch = "rstudio-launch-conditional",
  repo_name = "jhudsl/AnVIL_Template"
)
```

### With variables set:

```{r, echo = FALSE, results='asis'}
AnVIL_module_settings <- list(
  audience = "student",
  docker_image = "test docker",
  startup_script = "test startup script"
)

cow::borrow_chapter(
  doc_path = "child/_child_rstudio_launch.Rmd",
  branch = "rstudio-launch-conditional",
  repo_name = "jhudsl/AnVIL_Template"
)
```
