# Student instructions

Modules aimed at students in a course or workshop.
 
<br>
 
## Student Account Setup
 
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_student_create_account.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```

## Student instructions for launching RStudio

These instructions can be customized by setting certain variables before running `cow::borrow_chapter()`. Developers should create these variables as a list `AnVIL_module_settings`. The following variables can be provided:

- `audience` = Defaults to `general`, telling them to use the default RStudio settings. If `audience` is set to `student`, it gives more specific instructions.
- `docker_image` = Optional, it will tell them to open the customization dialogue and direct them on how to set the image.
- `startup_script` =  Optional, it will tell them to open the customization dialogue and direct them on how to set the script.

### Using default RStudio environment:

```{r, echo = FALSE, results='asis'}
AnVIL_module_settings <- list(
  audience = "student"
)

cow::borrow_chapter(
  doc_path = "child/_child_rstudio_launch.Rmd",
  branch = "rstudio-launch-conditional",
  repo_name = "jhudsl/AnVIL_Template"
)
```

### Using custom RStudio environment:

```{r, echo = FALSE, results='asis'}
AnVIL_module_settings <- list(
  audience = "student",
  docker_image = "example docker",
  startup_script = "example startup script"
)

cow::borrow_chapter(
  doc_path = "child/_child_rstudio_launch.Rmd",
  branch = "rstudio-launch-conditional",
  repo_name = "jhudsl/AnVIL_Template"
)
```
