# Student instructions

Modules aimed at students in a course or workshop.
 
<br>
 
## Student Account Setup
 
:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_student_create_account.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Student instructions for cloning a Workspace

These instructions can be customized to a specific workspace by setting certain variables before running `cow::borrow_chapter()`.  If these variables have not been set, reasonable defaults are provided (e.g. "ask your instructor").

### With no variables set:

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_student_workspace_clone.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

### With variables set:

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
# Specify variables
AnVIL_module_settings <- list(
  workspace_name = "Example_Workspace",
  workspace_link = "http://example.com/",
  billing_project = "Example Billing Project"
)

cow::borrow_chapter(
  doc_path = "child/_child_student_workspace_clone.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

## Student instructions for launching RStudio

The module below is specially customized for students, allowing you to give more specific instructions on the settings for their RStudio environment.  There are several other general purpose modules that may also be useful for students (e.g. Pausing RStudio, Deleting RStudio) that can be found in other chapters of this book.

The following instructions can be customized by setting certain variables before running `cow::borrow_chapter()`. Developers should create these variables as a list `AnVIL_module_settings`. The following variables can be provided:

- `audience` = Defaults to `general`, telling them to use the default RStudio settings. If `audience` is set to `student`, it gives more specific instructions.
- `docker_image` = Optional, it will tell them to open the customization dialogue and direct them on how to set the image.
- `startup_script` =  Optional, it will tell them to open the customization dialogue and direct them on how to set the script.

### Using default RStudio environment:

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
# Specify variables
AnVIL_module_settings <- list(
  audience = "student"
)

cow::borrow_chapter(
  doc_path = "child/_child_rstudio_launch.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

### Using custom RStudio environment:

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
# Specify variables
AnVIL_module_settings <- list(
  audience = "student",
  docker_image = "example docker",
  startup_script = "example startup script"
)

cow::borrow_chapter(
  doc_path = "child/_child_rstudio_launch.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::
