
1. The right-hand side icon reminds you that you are accruing cloud computing costs. If you don’t see this icon, you may need to scroll to the right.

    ```{r, echo=FALSE, out.width = '100%', fig.alt='Screenshot of the RStudio interface. The icon on the right showing that the cloud environment is running is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1BLTCaogA04bbeSD1tR1Wt-mVceQA6FHXa8FmFzIARrg/edit#slide=id.g11f12bc99af_0_84")
    ```

1. You should minimize charges when you are not performing an analysis. You can do this by clicking on the RStudio icon and selecting “Pause”. This will release the CPU and memory resources for other people to use. Note that your work will be saved in the environment and continue to accrue a very small cost.  This work will be lost if the cloud environment gets deleted.  If there is anything you would like to save permanently, it's a good idea to copy it from your compute environment to another location, such as the Workspace bucket, GitHub, or your local machine, depending on your needs.

    ```{r, echo=FALSE, out.width = '100%', fig.alt='Screenshot of the RStudio menu. The pause button which stops the cloud environment is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1BLTCaogA04bbeSD1tR1Wt-mVceQA6FHXa8FmFzIARrg/edit#slide=id.g11f12bc99af_0_91")
    ```

:::{.notice}
You can also pause your cloud environment(s) at https://anvil.terra.bio/#clusters.
:::
