1. [Launch Terra](https://anvil.terra.bio/#workspaces) and sign in with your Google account.  If this is your first time logging in to Terra, you will need to accept the Terms of Service.

1. In the drop-down menu on the left, navigate to "Billing". Click the triple bar in the top left corner to access the menu. Click the arrow next to your name to expand the menu, then click "Billing".  You can also navigate there directly with this link: https://anvil.terra.bio/#billing

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra drop-down menu.  Three items are highlighted: 1) the "hamburger" button for extending the drop-down menu, 2) the arrow next to your username, for extending the drop-down submenu, and 3) the submenu item "Billing".'}
ottrpal::include_slide("https://docs.google.com/presentation/d/10-YvYQqI2y32ErihJJMbyLAL4nPIkPA2MLk_6Ee7fXw/edit#slide=id.g116f8d759be_0_2")
    ```

1. Click “Owned by You” and find the Billing Project.  If you do not see the Billing Project in this list, then you are not an Owner and do not have permission to add members.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing Projects menu.  The submenu "Owned by you" is highlighted and has been expanded, showing a list of Billing Projects below.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/10-YvYQqI2y32ErihJJMbyLAL4nPIkPA2MLk_6Ee7fXw/edit#slide=id.g116f8d759be_0_149")
    ```

1. Click on the name of the Billing Project.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing Projects menu.  The submenu has been expanded, and the name of one of the Billing Projects is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/10-YvYQqI2y32ErihJJMbyLAL4nPIkPA2MLk_6Ee7fXw/edit#slide=id.g1edc2edcaf8_1_29")
    ```

1. Click on the “Members” tab to view and manage members.  Then click the “Add User” button.

    ```{r, echo=FALSE, fig.alt='Screenshot of a Terra Billing Project management page.  The tab labeled "Members" is highlighed and has been selected, and the button labeled "Add User" is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/10-YvYQqI2y32ErihJJMbyLAL4nPIkPA2MLk_6Ee7fXw/edit#slide=id.g1edc2edcaf8_1_14")
    ```
    
1. Enter the email address of the user or group you’d like to add the the Billing Project.
    - If adding an individual, make sure to enter the account that they use to access AnVIL.
    - If adding a Terra Group, use the Group email address, which can be found on the Terra Group management page.

    ```{r, echo=FALSE, fig.alt='Screenshot of a Terra Billing Project management page.  The tab labeled "Members" is highlighed and has been selected, and the button labeled "Add User" is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/10-YvYQqI2y32ErihJJMbyLAL4nPIkPA2MLk_6Ee7fXw/edit#slide=id.g1edc2edcaf8_1_14")
    ```
